Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-02-28 paper/paper.tex
pass

\begin{table*}[t!]
  \small
  \caption{\label{table:attacks}List of attacks.}
  \centering
  \begin{tabular}{llllp{10cm}}
    \toprule
    \multicolumn{1}{c}{Name} &
    \multicolumn{1}{c}{Source} &
    \multicolumn{1}{c}{Type} &
    \multicolumn{1}{c}{Protocol} &
    \multicolumn{1}{c}{Groud Truth (relevant/checked options)} \\
    \midrule     
    Ping Scan & NMAP & AREC & ICMP & \textbf{dsize}:0; \textbf{itype}:8; \\
    SYN Flood & hping3 & DoS & TCP & \textbf{flags}: S,12; \textbf{threshold}: type both, track by\_dst, count 5000, seconds 5;\\

    JBoss JMX\MyComment{ Console Beanshell Exploit} & Nikto2 & RCE & HTTP \MyComment{& Remote Code Execution} & \textbf{content}:"/HtmlAdaptor"; nocase; http\_uri; \textbf{content}:"action=inspect"; nocase; http\_uri; \textbf{content}:"bean"; nocase; http\_uri; \textbf{content}:"name="; http\_uri; \\
    WeBid \MyComment{Local File Inclusion} & RFI & HTTP & \Fix{LFI} & \textbf{content}:"GET "; depth:4; \textbf{content}:"/cron.php?"; http\_uri; nocase; \textbf{content}:"include\_path="; http\_uri; nocase; \textbf{content}:"../"; \\
    ColdFusion \MyComment{PESC} & Nikto2 & PESC & HTTP \MyComment{& Privilege Escalation} & \textbf{content}:"GET"; http\_method; nocase; \textbf{content}:"/CFIDE/administrator"; http\_uri; nocase; \\
    .htaccess access\MyComment{attempted-recon} & Nikto2 & AREC & HTTP \MyComment{& Adicionar} & \textbf{content}:".htaccess"; nocase; http\_uri; \\
    .idq access\MyComment{EXPLOIT ISAPI} & Nikto2 & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:".idq"; nocase; http\_uri; \\
    iisadmin access\MyComment{web-application-attack} & Nikto2 & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:"/iisadmin"; nocase; http\_uri; \\
    /system32/ in URI\MyComment{Possible Protected Directory Access Attempt} & Nikto2 & AREC & HTTP \MyComment{& Adicionar} & \textbf{content}:"/system32/"; nocase; http\_uri; \\
    Script tag in URI\MyComment{Possible Cross Site Scripting Attempt} & Nikto2 & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:"</script>"; nocase; http\_uri; \\
    Apache Struts 2 & \Fix{Source} & \Fix{RCE} & HTTP & \textbf{content}:"POST"; http\_method; \textbf{content}:"java.lang.ProcessBuilder"; nocase; http\_client\_body; fast\_pattern; \textbf{content}:"/struts2-rest-showcase/orders/3"; http\_uri; \\
    WordPress Login & \Fix{Source} & Policy Violation & HTTP & \textbf{content}:"log="; http\_client\_body; \textbf{content}:"\&pwd="; http\_client\_body; \textbf{content}:"\&wp-submit="; http\_client\_body; \\
    \bottomrule
  \end{tabular}
\end{table*}

@@

\vspace{1ex}
\subsubsection{Attacks.}~Table~\ref{table:attacks} shows the selection
of attacks considered in our evaluation.  Column ``Name'' shows the
name of the attack, column ``Source'' shows the source where we
obtained data to reproduce the attack (see
Section~\ref{subsec:malicious-traffic}), column ``Type'' shows the
kind of attack, column ``Protocol'' shows the name of the protocol
explored in the attack, and column ``Ground Truth'' shows the rule
options to capture the attack. The rationale for the selection were
(1) to cover attacks with different characteristics, (2) to cover
attacks of various protocols, and (3) to explore different features of
\tname. As for (1), the selection includes attacks of the following
types: Denial-of-Service (DoS), Active Reconnaissance (AREC),
Privilege escalation (PESC), Remote Code Execution (RCE), \Luc{Local 
File Inclusion (LFI) and Policy Violation (PV)}. Note that the 
distribution of attacks is not uniform across protocols as these 
distributions are not uniform in practice---http attacks are prevalent.

>>>>

\begin{table*}[t!]
  \small
  \caption{\label{table:attacks}List of attacks.}
  \centering
  \begin{tabular}{llllp{10cm}}
    \toprule
    \multicolumn{1}{c}{Name} &
    \multicolumn{1}{c}{Source} &
    \multicolumn{1}{c}{Type} &
    \multicolumn{1}{c}{Protocol} &
    \multicolumn{1}{c}{Groud Truth (relevant/checked options)} \\
    \midrule     
    Ping Scan & NMAP & AREC & ICMP & \textbf{dsize}:0; \textbf{itype}:8; \\
    SYN Flood & hping3 & DoS & TCP & \textbf{flags}: S,12;
    \textbf{threshold}: type both, track by\_dst, count 5000, seconds
    5;\\
    \midrule
    JBoss JMX\MyComment{ Console Beanshell Exploit} & Nikto2 & RCE & HTTP \MyComment{& Remote Code Execution} & \textbf{content}:"/HtmlAdaptor"; nocase; http\_uri; \textbf{content}:"action=inspect"; nocase; http\_uri; \textbf{content}:"bean"; nocase; http\_uri; \textbf{content}:"name="; http\_uri; \\
    WeBid \MyComment{Local File Inclusion} & RFI & LFI & HTTP & \textbf{content}:"GET "; depth:4; \textbf{content}:"/cron.php?"; http\_uri; nocase; \textbf{content}:"include\_path="; http\_uri; nocase; \textbf{content}:"../"; \\
    ColdFusion \MyComment{PESC} & Nikto2 & PESC & HTTP \MyComment{& Privilege Escalation} & \textbf{content}:"GET"; http\_method; nocase; \textbf{content}:"/CFIDE/administrator"; http\_uri; nocase; \\
    .htaccess access\MyComment{attempted-recon} & Nikto2 & AREC & HTTP \MyComment{& Adicionar} & \textbf{content}:".htaccess"; nocase; http\_uri; \\
    .idq access\MyComment{EXPLOIT ISAPI} & Nikto2 & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:".idq"; nocase; http\_uri; \\
    iisadmin access\MyComment{web-application-attack} & Nikto2 & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:"/iisadmin"; nocase; http\_uri; \\
    /system32/ in URI\MyComment{Possible Protected Directory Access Attempt} & Nikto2 & AREC & HTTP \MyComment{& Adicionar} & \textbf{content}:"/system32/"; nocase; http\_uri; \\
    Script tag in URI\MyComment{Possible Cross Site Scripting Attempt} & Nikto2 & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:"</script>"; nocase; http\_uri; \\
    Apache Struts 2 & \Fix{Source} & RCE & HTTP & \textbf{content}:"POST"; http\_method; \textbf{content}:"java.lang.ProcessBuilder"; nocase; http\_client\_body; fast\_pattern; \textbf{content}:"/struts2-rest-showcase/orders/3"; http\_uri; \\
    WordPress Login & \Fix{Source} & PVE & HTTP & \textbf{content}:"log="; http\_client\_body; \textbf{content}:"\&pwd="; http\_client\_body; \textbf{content}:"\&wp-submit="; http\_client\_body; \\
    \bottomrule
  \end{tabular}
\end{table*}

@@

\vspace{1ex}
\subsubsection{Attacks.}~Table~\ref{table:attacks} shows the selection
of attacks we analyzed. Column ``Name'' shows the name of the attack,
column ``Source'' shows the source where we obtained data to reproduce
the attack (see Section~\ref{subsec:malicious-traffic}), column
``Type'' shows the kind of attack, column ``Protocol'' shows the name
of the protocol explored in the attack, and column ``Ground Truth''
shows the rule options to capture the attack. The rationale for the
selection were (1) to cover attacks with different characteristics,
(2) to cover attacks of various protocols, and (3) to explore
different features of \tname. As for (1), the selection includes
attacks of the following types: Denial-of-Service
(DoS)~\cite{denial-of-service}, Active Reconnaissance
(AREC)~\cite{active-reconnaissance}, Privilege escalation
(PVE)~\cite{privilege-escalation}, Remote Code Execution
(RCE)~\cite{remote-code-execution}, Local File Inclusion
(LFI)~\cite{local-file-inclusion}, and Policy Violation
(PV)~\Fix{local-file-inclusion}. Note that the distribution of attacks
is not uniform across protocols as these distributions are not uniform
in practice---http attacks are prevalent.
